Tidal streams in triaxial systems

### 2015-02-02 ms.tex
working on introduction

% packages
\usepackage{amssymb,amsmath,amsbsy}

@@

>>>>

% packages
\usepackage{amssymb,amsmath,amsbsy}
\usepackage{forest}

@@

For an integrable Hamiltonian, $H$, with $N$ degrees of freedom (d.o.f.), the equations of motion are most simply expressed in angle-action coordinates. In these coordinates, the actions, $J_n$, are integrals of the motion, and the conjugate angle variables, $\theta_n$, increase linearly with time
\begin{align}
	J_n &= {\rm const.}\\
	\dot{J}_n &= -\frac{\partial H}{\partial \theta_n} = 0\\
	\theta_n(t) &= \Omega_n t + \theta_n(0)\\
	\dot{\theta}_n &= \frac{\partial H}{\partial J_n} = \Omega_n(J_1,...,J_n)
\end{align}
where $n=1,2,...N$, and $\Omega_n$ are the fundamental frequencies of the orbit. Owing to the involutive property of the actions and the periodic nature of the angle variables, the topology of angle-action space is equivalent to that of the surface of an $N$-dimensional torus, and thus orbits are often referred to in terms of \emph{orbital tori}; each set of actions, $(J_1,J_2,...J_N)$, uniquely determine the torus associated with a given orbit.

If galactic halos are triaxial, their gravitational potentials will almost certainly not be globally integrable. For a given halo, if the potential is close to integrable such that the Hamiltonian can be written in terms of a small perturbation, $\epsilon$, away from some integrable Hamiltonian, $H_0$,
\begin{equation}
	H(\bs{\theta}, \bs{J}) = H_0(\bs{J}) + \epsilon H_1(\bs{\theta}, \bs{J})
\end{equation}
then a large number of regular orbits will survive the perturbation (e.g., the KAM theorem; cite Arnold)\footnote{3-vectors are represented with bold symbols}. The tori that survive will in general by separated by regions of irregular or chaotic motion, and thus any transformations to angle-action coordinates can only be defined locally. The types of motion generic to typical triaxial systems can be split into several sub-categories (summarized in Figure~\ref{fig:orbit-tree}). Regular motion can be classified by the number of resonance relations it obeys \citep[e.g.,][]{valluri98}: \emph{quasi-periodic} orbits obey no resonance relations, \emph{uni-resonant} orbits obey a single relation of the form $\bs{m}\cdot\bs{\Omega}=0$, and \emph{bi-resonant} orbits obey two resonance relations, $\bs{m}\cdot\bs{\Omega}=0$ and $\bs{n}\cdot\bs{\Omega}=0$, where $\bs{m}$ and $\bs{n}$ are integer vectors.

\begin{figure*}[!h]
\begin{center}
\includegraphics[width=0.5\textwidth]{figures/orbit-tree.pdf}
\caption{} \label{fig:orbit-tree}
\end{center}
\end{figure*}

For small perturbations, quasi-periodic, resonant, and periodic orbits all survive. As the strength of the perturbation increases, the tori associated with quasi-periodic motion

the (bold symbols represent 3-vectors)

\section{Numerical methods}

\subsection{Numerical estimation of fundamental frequencies}

\subsection{Particle balls}

\section{Experiments}

\subsection{Potential choice}

\subsection{Frequency map}

\subsection{Morphology}

\subsection{Morphology}
